Forecasting biodiversity in breeding birds using best practices

### 2017-12-11 manuscript/draft.Rmd

The most commonly used methods for forecasting future biodiversity, SDMs and
macroecological models, both produced worse forecasts than time-series models
and simple baselines. This weakness suggests that predictions about future
biodiversity change should be viewed with skepticism unless the underlying
models have been validated temporally, via hindcasting and comparison with
simple baselines. Since site-level richness is relatively stable, spatial
validation is not enough: a model can have high accuracy across spatial
gradients without being able to predict changes over time. This gap between
spatial and temporal accuracy is known to be important for species-level
predictions [@rapacciuolo2012; @oedekoven2017]; our results indicate that it is
substantial for higher-level patterns like richness as well. SDMs' poor temporal
predictions are particularly sobering, as these models have been one of the main
foundations for estimates of the predicted loss of biodiversity to climate
change over the past decade or so [@thomas2004; @thuiller2011; @urban2015]. Our
results also highlight the importance of comparing multiple modeling approaches
when conducting ecological forecasts, and in particular, the value of comparing
results to simple baselines to avoid over-interpreting the information present
in these forecasts [Box 1]. Disciplines that have more mature forecasting
cultures often do this by reporting "forecast skill", i.e., the improvement in
the forecast relative to a simple baseline [@jolliffe2003]. We recommend
following the example of @ye2015 and adopting this approach in future ecological
forecasting research.

@@

Typically ecological forecasts use one modeling approach or a small number of
related approaches. By fitting and evaluating multiple modeling approaches we
can learn more rapidly about the best approaches for making predictions for a
given ecological quantity [@clark2001; @ward2014]. This includes comparing
process-based [e.g., @kearney2009] and data-driven models [e.g., @ward2014], as
well as comparing the accuracy of forecasts to simple baselines to determine if
the modeled forecasts are more accurate than the naive assumption that the world
is static [@jolliffe2003; @ye2015].

>>>>

The most commonly used methods for forecasting future biodiversity, SDMs and
macroecological models, both produced worse forecasts than time-series models
and simple baselines. This weakness suggests that predictions about future
biodiversity change should be viewed with skepticism unless the underlying
models have been validated temporally, via hindcasting and comparison with
simple baselines. Since site-level richness is relatively stable, spatial
validation is not enough: a model can have high accuracy across spatial
gradients without being able to predict changes over time. This gap between
spatial and temporal accuracy is known to be important for species-level
predictions [@rapacciuolo2012; @oedekoven2017]; our results indicate that it is
substantial for higher-level patterns like richness as well. SDMs' poor temporal
predictions are particularly sobering, as these models have been one of the main
foundations for estimates of the predicted loss of biodiversity to climate
change over the past decade or so [@thomas2004; @thuiller2011; @urban2015]. Our
results also highlight the importance of comparing multiple modeling approaches
when conducting ecological forecasts, and in particular, the value of comparing
results to simple baselines to avoid over-interpreting the information present
in these forecasts [Box 1]. Disciplines that have more mature forecasting
cultures often do this by reporting "forecast skill", i.e., the improvement in
the forecast relative to a simple baseline [@jolliffe2003]. We recommend
following the example of @perretti2013 and adopting this approach in future
ecological forecasting research.

@@

Typically ecological forecasts use one modeling approach or a small number of
related approaches. By fitting and evaluating multiple modeling approaches we
can learn more rapidly about the best approaches for making predictions for a
given ecological quantity [@clark2001; @ward2014]. This includes comparing
process-based [e.g., @kearney2009] and data-driven models [e.g., @ward2014], as
well as comparing the accuracy of forecasts to simple baselines to determine if
the modeled forecasts are more accurate than the naive assumption that the world
is static [@jolliffe2003; @perretti2013].
